Filtering in the flowCore package

### 2006-12-11 inst/doc/filtering-flowCore.Rnw
* allow filter to return different types of class based on the input type. This will eventually allow the return of randomResultType for soft clustering operations.
* started adding split() and Subset() (the default R subset is not currently compatible with S4) methods for flowFrame to obtain flowSets based on gates.

* added a compensate() method for flowFrames and flowSets that returns a new frame or set adjusted by a spillover matrix.

* added a spillover method that tries to automatically calculation a spillover matrix from a set of comp beads/cells. This is a work in progress.

git-svn-id

>>>>

\section{Implementing New Filters}

Implementing a new filter is a fairly straightforward process requiring the definition of a filtering class, derived from the \Rclass{filter} base class, and, at the minimum, the definition of an \Rfunction{%in%} method.

\subsection{Customzing a \Robject{filter} class}

A \Robject{filter} subclass can be customized in one of two ways. First, the class returned by the \Rfunction{filter} method can be changed by definiting a \Rfunction{filterResultType} method for your filter class. This allows filters that return non-deterministic results (e.g. soft-clustering filters) to use the \Rclass{randomFilterResult}.
